### 2019-11-15 analysis/output/include/path_diagram_full.tex
Updated flow chart of data cleaning

\begin{tikzpicture}[auto,scale=2, 
	observed/.style={rectangle,draw,thick,inner sep=5pt,minimum size=1cm, align=center},
	latent/.style={circle, draw, thick, inner sep=0pt, minimum size=2cm, align=center}, 
	path/.style={->, thick, >=stealth'},
	loading/.style={->, thick, dashed, >=stealth'}]

@@

\coordinate[below= 0.7in of s] (somid);
\node [observed] (sc) [left = 0.5in of somid] {SOC};
\node [observed] (ss) at (somid) {Sand};
\node [observed] (so) [right = 0.5in of somid] {CEC};

@@

\draw [loading] (m) to node[left, pos=0.5] {\pcfmmp{}} (mp);
\draw [loading] (m) to node[left, pos=0.5] {\pcfmmpc{}} (mpc);
\draw [loading] (m) to node[right, pos=0.5] {\pcfmmt{}} (mt);
\draw [loading] (m) to node[right, pos=0.5] {\pcfmmtc{}} (mtc);

\draw [loading] (s) to node[left, pos=0.5] {\pcfssc{}} (sc);
\draw [loading] (s) to node[left, pos=0.5] {\pcfsss{}} (ss);
\draw [loading] (s) to node[right, pos=0.5] {\pcfsso{}} (so);

\draw [loading] (d) to node {\pcfdds{}} (ds);
\draw [loading] (d) to node[left, pos=0] {\pcfdde{}} (de);

\draw [loading] (h) to node[] {\pcfhhd{}} (hd);
\draw [loading] (h) to node {\pcfhhh{}} (hh);

>>>>

\begin{tikzpicture}[auto,scale=2, 
	observed/.style={rectangle,draw,thick,inner sep=5pt,minimum size=1cm, align=center},
	latent/.style={circle, draw, thick, inner sep=0pt, minimum size=2cm, align=center}, 
	path/.style={->, thick, >=stealth'},
	loading/.style={->, thick, dotted, >=stealth'},
	loadingset/.style={->, thick, dashed, >=stealth'}]

@@

\coordinate[below= 0.7in of s] (somid);
\node [observed] (ss) [left = 0.5in of somid] {Sand};
\node [observed] (sc) at (somid) {SOC};
\node [observed] (so) [right = 0.5in of somid] {CEC};

@@

\draw [loadingset] (m) to node[left, pos=0.5] {\pcfmmp{}} (mp);
\draw [loading] (m) to node[left, pos=0.5] {\pcfmmpc{}} (mpc);
\draw [loading] (m) to node[right, pos=0.5] {\pcfmmt{}} (mt);
\draw [loading] (m) to node[right, pos=0.5] {\pcfmmtc{}} (mtc);

\draw [loadingset] (s) to node[left, pos=0.5] {\pcfsss{}} (ss);
\draw [loading] (s) to node[left, pos=0.5] {\pcfssc{}} (sc);
\draw [loading] (s) to node[right, pos=0.5] {\pcfsso{}} (so);

\draw [loadingset] (d) to node {\pcfdds{}} (ds);
\draw [loading] (d) to node[left, pos=0] {\pcfdde{}} (de);

\draw [loading] (h) to node[] {\pcfhhd{}} (hd);
\draw [loadingset] (h) to node {\pcfhhh{}} (hh);
